---
output: github_document
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "85%",
  eval=FALSE
)
```

# GIStoolkit

`GIStoolkit`is a collection of handy R functions for accomplishing common GIS tasks. 

## Installation

You can install the development version of GIStoolkit from [GitHub](https://github.com/) with:

```r
remotes::install_github("QAWalker/GIStoolkit")

```

## Load the package into your R session
```r
library(GIStoolkit)

```

## Functions

### 1. Interactive Point Selection
`get_clicked_point()` launches an interactive map in your viewer or browser and allowing the user to save the clicked point. You must click the marker icon on the left to add a point.

```{r select-point, eval=FALSE}
my_point <- get_clicked_point()
```

### 2. Interactive Raster Cropping
`click_to_crop(raster_obj, mask = TRUE)`allows you to define a study area visually.

**The `mask`parameter determines the output:**

* **`mask = TRUE`(Default):** Launches a **polygon** tool. The result is clipped to the exact shape, and pixels outside are set to `NA`.
* **`mask = FALSE`:** Launches an **extent** tool. The result is cropped to a rectangular bounding box.

```{r crop-raster, eval=FALSE}
r <- terra::rast("my_raster.tif")

# To get a polygon shape:
polygon_crop <- click_to_crop(r, mask = TRUE)

# To crop to a rectangular defined by the extend of the points:
rectangle_crop <- click_to_crop(r, mask = FALSE)

# Save Cropped Results
terra::writeRaster(polygon_crop, filename = "path/to/save/polygon_cropped_raster.tif")

terra::writeRaster(rectangle_crop, filename = "path/to/save/rectangle_cropped_raster.tif")

```

### 3. Generate Points Along a Line
`generate_line_points(line_sf, distance, crs = 5070)` samples evenly spaced points along an `sf` linestring at a given meter interval, including the start and end of the line. Input can come from a KML/KMZ file exported from Google Earth via `kml_to_polyline()`.

```{r generate-line-points, eval=FALSE}
my_line <- kml_to_polyline("path/to/file.kml")

# Place a point every 100 meters (default CONUS Albers CRS)
pts <- generate_line_points(my_line, distance = 100)

# Use UTM Zone 18N for higher accuracy on the US East Coast
pts <- generate_line_points(my_line, distance = 100, crs = 32618)
```

The returned `sf` object contains a `point_id` column (sequence along the line) and a `distance_m` column (cumulative distance from the start).
